Shiny Walkthrough

### 2020-06-22 analysis/shiny_walkthrough.Rmd
Added a flexdashboard section - fixed issues so it works properly

```{r}
selectInput(
  inputId = "object", # This is the name you described the object elsewhere in the application
  label = "Favorite Character", # The label you want to show to the user
  choices = c(starwars$name) # List the choices the user has to pick from
 )
```

>>>>

```{r}
library("shiny")
library("tidyverse")
selectInput(
  inputId = "object", # This is the name you described the object elsewhere in the application
  label = "Favorite Character", # The label you want to show to the user
  choices = c(starwars$name) # List the choices the user has to pick from
 )
```
